Untitled

### 2025-02-24 script/r/draft.Rmd
draft: desert control rds

```{r}
tiff_file <- "C:/Users/Redha CHABA/Desktop/temp/desert.tif"

@@

freq(binary_raster)

plot(binary_raster, main = "Desert Map", col = terrain.colors(100))

@@

```{r}
library(ggplot2)

ggplot(data_final_nlp_bis2%>%filter(!is.na(neig_eth_a)), aes(x = factor(neig_eth_a))) +
  geom_bar(fill = "steelblue") +
  labs(title = "Willingness to Have Neighbors of Different Ethnicities - Waves 6-8",
       y = "Count",
       x=NULL) +
  scale_x_discrete(labels = c("Strongly dislike", "Somewhat dislike","Would not care", "Somewhat like", "Strongly like")) +
  theme_minimal()

ggplot(data_final_nlp_bis2%>%filter(!is.na(neig_eth_a), spl==1), aes(x = factor(neig_eth_a))) +
  geom_bar(fill = "steelblue") +
  labs(title = "Willingness to Have Neighbors of Different Ethnicities - Waves 6-8",
       y = "Count",
       x=NULL) +
  scale_x_discrete(labels = c("Strongly dislike", "Somewhat dislike","Would not care", "Somewhat like", "Strongly like")) +
  theme_minimal()
```

>>>>

```{r}
library(terra)

tiff_file <- "data/data_raw/geography/desert/desert.tif"

@@

plot(binary_raster, main = "Desert Map", col = rev(heat.colors(100)))

@@
